Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Changes in Conclusions and Future Work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
On this paper it was presented how to define a stable novelty threshold function on
top of \emph{probabilistic graphical models} instantiated dynamically from sensed
semantic data.
The presented technique is based on the ratio between a conditional and
unconditional probability and when perfect information exists it performs an optimal
novelty detection threshold.

It was also shown that a correct estimation of unconditional probability plays an
important role specially on small input spaces. And that semi-supervised techniques
implemented with the access to unlabelled data can be used to significantly improve
novelty detection performance.

On the used synthetic distribution, an assumption on an uniform
distribution has led to very poor results. This same behaviour is expected to held
in real world distributions also based on semantic data. And for that reason
and due to easy access to unlabelled data special attention will be given on using
semi-supervised techniques for novelty detection.

After this initial study on how to detect new semantic classes based on
\emph{graphical models} future work will focus on how to use the structured
information available from the conceptual layer and be able to detect which variable
of the graph is novel and what makes it different from other previously learned
classes. That will lead to generation of useful information that can be used on
communication with the user and perform active learning of new room categories.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
In this paper we presented how to define a stable novelty threshold function on
top of \emph{probabilistic graphical models} instantiated dynamically from sensed
semantic data.
The presented technique is based on the ratio between a conditional and
unconditional probability and when perfect information exists it performs an optimal
novelty detection threshold.

It was also shown that a correct estimation of unconditional probability plays an
important role specially on small input spaces. Moreover, semi-supervised techniques
implemented with the access to unlabelled data can be used to significantly improve
novelty detection performance.

Given the synthetic distribution, an assumption on an uniform
distribution has led to very poor results. The same behaviour is expected to
in real world distributions based on semantic data. For that reason,
and due to easy access to unlabelled data, special attention will be given to using
semi-supervised techniques for novelty detection.

After this initial study on how to detect new semantic classes based on
graphical models, future work will focus on how to use the structured
information available from the conceptual layer to be able to detect which variable
of the graph is novel and what makes it different from other previously learned
classes. That will lead to generation of useful information that can be used for
communication with the user and performing active learning of new room categories.
